TBD

### 2021-02-21 outputs/paper/paper.Rmd
Add caption to 'tableChisq' function

### Format table for Chi-squared test
tableChisq <- function(stat, df, p) {   
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p)
  chi_df <- data.frame(chi_stat, chi_param, chi_p)

  kable(chi_df,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    kable_paper(c("striped", "hover"))
}

@@

tableChisq(q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```

>>>>

### Format table for Chi-squared test
tableChisq <- function(capt, stat, df, p) {   
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p)
  chi_df <- data.frame(chi_stat, chi_param, chi_p)

  kable(chi_df,
        digits = 2,
        caption = capt,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    kable_paper(c("striped", "hover"))
}

@@

tableChisq(q14_chi$method, q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
